Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-26 ms.tex
revisions

\author{Andrew Emerick}
\affil{Columbia University}
\affil{American Museum of Natural History (AMNH)}

@@

\author{Mordecai-Mark Mac Low}
\affiliation{American Museum of Natural History (AMNH)}
\nocollaboration

@@

This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates in each simulation. As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation. Because of this difference in SFR, the mass loading factor differences across simulations ($\eta = \dot{M}_{\rm out} / <\rm{SFR}>_{100 \rm{Myr}}$) are more significant. While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this, while noRT is even lower. The fiducial run is also the only one of the three with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius. The outflow in noRT is nearly the same as the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback. We conclude that radiation feedback allows SN to be substantially more effective in driving outflows. We provide a physical explanation for these differences in the following section.

\begin{figure*}
\centering
\includegraphics[width=0.32\linewidth]{metal_retention}
\includegraphics[width=0.32\linewidth]{mass_outflow_comparison} 
\includegraphics[width=0.32\linewidth]{mass_loading_comparison}
\caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange). As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively. {\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed). {\bf Right:} The mass loading factor, calculated as the outflow rate divided by 100~Myr averaged SFR. }
\label{fig:metal_retention}
\end{figure*}

>>>>

\author{Andrew Emerick}
\affil{Columbia University}
\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}

@@

\author{Mordecai-Mark Mac Low}
%mm [I've been asked to use my Columbia affiliation when working with CU students]
\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
\affiliation{Columbia University}

\nocollaboration

@@

This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates in each simulation. As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation. Because of this difference in SFR, 
%mm [rewrote to display equation]
the differences across simulations are more significant for our computed mass loading factor 
\begin{equation}
    \eta = \dot{M}_{\rm out} / <\rm{SFR}>_{100 \rm{Myr}}
\end{equation}. The brackets indicate time averaging over 100~Myr.
%
While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this, while noRT is even lower.

%mm [ended the paragraph to leave the previous important sentence in the place of emphasis at the end of the paragraph.]
The fiducial run is also the only one of the three with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius. The outflow in noRT is 
%mm nearly the same as 
   only a factor of a few lower than 
the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, 
%mm 
    so it implies a far lower mass loading factor. 
We conclude that radiation feedback allows SNe to be substantially more effective in driving outflows. 
%mm We provide a physical explanation for these differences in the following section.

\begin{figure*}
\centering
\includegraphics[width=0.32\linewidth]{metal_retention}
\includegraphics[width=0.32\linewidth]{mass_outflow_comparison} 
\includegraphics[width=0.32\linewidth]{mass_loading_comparison}
\caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange). As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively. {\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed). {\bf Right:} The mass loading factor $\eta$ calculated as the outflow rate divided by the SFR averaged over 100~Myr. 
%mm
   Inclusion of diffuse ionization makes an order of magnitude difference in $\eta$ in 
   this case. }
\label{fig:metal_retention}
\end{figure*}
